---
title: "MZ Data & Policy Studio"
output:
  github_document: default
  word_document: default
---

# Setting up the document 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Will install packages if first time

```{r eval=FALSE}
# Best to leave these commented out
# install.packages('dplyr')
# install.packages('readr')
# install.packages('tidyr')
# install.packages('stringr')
# install.packages('forcats')
# install.packages('purr')
# install.packages('ggpubr')
# install.packages('car')
# install.packages('gdata')
# install.packages('skimr')
# install.packages('readxl')
# install.packages('scales')
# install.packages('janitor')
# install.packages('gtsummary')
# install.packages('srvyr')
# install.packages('broom')
# install.packages('ggstance')
# install.packages("margins")
# install.packages('haven')
```

# Read in the packages needed
```{r message=FALSE}
library(readr) # read/write dataframes
library(tidyr) # reshaping dataframes
library(stringr) # string manipulation
library(forcats) # factor manipulation
library(purrr) # iteration (instead of loops)
library(ggpubr) # for Correlation
library(ggplot2) # for Plots
library(car)
library(gdata)
library(skimr)
library(readxl)
library(dplyr) # manipulate dataframes
library(janitor) # Clean data  
library(broom)
library(gtsummary)
library(srvyr)
library(ggstance)
library('margins')

```


# Import the data- ANES Survey Timeseries
# Unzip the ANES data if needed
```{r}
source("unzip-anes-data.r")
```

```{r}

# Importing the main data set from the American National Election Survey

library(haven)

anes_timeseries_cdf_stata13 <- read_dta("data-raw/anes_timeseries_cdf_stata13.dta") %>% 
  zap_labels() %>% 
  zap_formats()
```
# Filtering for the right years 
```{r}
Data_2004 <- anes_timeseries_cdf_stata13[!(anes_timeseries_cdf_stata13$VCF0004 < "2004"), ]

```

```{r}
# Removing Labels

Data_2004 %>%
  zap_labels() %>%
  select(
    VCF0102,
    VCF0104,
    VCF0880,
    VCF0606,
    VCF0501,
    VCF9030a,
    VCF9206,
    VCF0105b,
    VCF0450,
    VCF0301,
    VCF9206,
    VCF9202,
    VCF9257,
    VCF0358,
    VCF0360,
    VCF0370,
    VCF0372,
    VCF9253,
    VCF0714,
    VCF9256,
    VCF0900b,
    VCF0114,
    VCF9021,
    VCF9030b,
    VCF9030c,
    VCF9222,
    VCF0901a,
    VCF0009z,
    VCF0310,
    VCF0358,
    VCF0360,
    VCF0370,
    VCF0372,
    VCF0359,
    VCF0361,
    VCF0371,
    VCF0373,
    VCF0702,
  ) %>%
  skim()
```

Filtering the Dataset for the right variables

Dealing w/ missings # For many of the categories I added a "Dummy" category to signal the question was unanswered. If the regression shows these dummies are not significant, can assume that these missings were not strongly biased in a direction. 

```{r}

Filtered_DS <- Data_2004 %>% 
  select(
    VCF0004, 
    VCF0006,
    VCF0009z,
    VCF0102,
    VCF0104,
    VCF0105b,
    VCF0114,
    VCF0110,
    VCF0301,
    VCF0310,
    VCF0358,
    VCF0359,
    VCF0360,
    VCF0361,
    VCF0370,
    VCF0371,
    VCF0372,
    VCF0373,
    VCF0450,
    VCF0501,
    VCF0606,
    VCF0702,
    VCF0714,
    VCF0880,
    VCF0900b,
    VCF0901a,
    VCF9021,
    VCF9030a,
    VCF9030b,
    VCF9030c,
    VCF9201,
    VCF9202,
    VCF9206,
    VCF9222,
    VCF9257,
    VCF9256
) %>%
  dplyr::mutate(
    VCF0501 = replace_na(VCF0501, 9),
    VCF9257 = replace_na(VCF9257, 3),
    VCF9256 = replace_na(VCF9256, 3),
    VCF9030a =  replace_na(VCF9030a, 3),
    VCF9030b = replace_na(VCF9030b, 3),
    VCF9030c = replace_na(VCF9030c, 3),
    VCF0114 = replace_na(VCF0114, 6),
    VCF0310 = replace_na(VCF0310, 9),
    VCF9021 = replace_na(VCF9021, 3)
  ) %>% 
  rename(
    control_split = VCF9206,
    Voted_Y_N = VCF0702,
    Race = VCF0105b,
    Interest_Elec = VCF0310,
    Weights = VCF0009z,
    Community_work =VCF9257,
    Dem_Pres_Angry = VCF0358,
    Dem_Pres_hopeful = VCF0360,
    Rep_Pres_Angry = VCF0370,
    Rep_Pres_hopeful = VCF0372,
    Election_Close = VCF0714,
    Age = VCF0102,
    Gender = VCF0104,
    Better_worse = VCF0880,
    FED_Tax = VCF0606,
    Bw_parties = VCF0501,
    contacted_by_party = VCF9030a,
    Volunteer_work = VCF9256,
    State_CD = VCF0900b,
    Income = VCF0114,
    Contacted_Dem_Party = VCF9030b,
    Contacted_Rep_Party = VCF9030c,
    Country_direction = VCF9222,
    State = VCF0901a,
    Approve_President = VCF0450,
    Party = VCF0301,
    Education = VCF0110,
    Anyone_talk_vote = VCF9021,
    Like_dislike_Rep_party = VCF9202,
    YEAR = VCF0004,
    Dem_Pres_Afraid = VCF0359,
    Dem_Pres_Proud = VCF0361,
    Rep_Pres_Afraid = VCF0371,
    Rep_Pres_Proud = VCF0373,
    Like_dislike_Dem_party = VCF9201
  )
```

# Creating Dummy Variables
```{r}

Final_DS_DV <- Filtered_DS %>%
  mutate(
    Age_Dummy = factor(Age),
    Interest_elec_DV = factor(Interest_Elec),
    Gender_DV = factor(Gender),
    bw_parties_DV = factor(Bw_parties),
    Contacted_by_party_DV = factor(contacted_by_party),
    Contacted_Dem_Party_DV = factor(Contacted_Dem_Party),
    Contacted_Rep_Party_DV = factor(Contacted_Rep_Party),
    Control_split_DV = factor(control_split),
    Race_DV = factor(Race),
    Dem_Pres_Angry_DV = factor(Dem_Pres_Angry),
    Dem_Pres_hopeful_DV = factor(Dem_Pres_hopeful),
    Rep_Pres_Angry_DV = factor(Rep_Pres_Angry),
    Rep_Pres_hopeful_DV = factor(Rep_Pres_hopeful),
    Dem_Pres_Afraid_DV = factor(Dem_Pres_Afraid),
    Dem_Pres_Proud_DV = factor(Dem_Pres_Proud),
    Rep_Pres_Afraid_DV = factor(Rep_Pres_Afraid),
    Rep_Pres_Proud_DV = factor(Rep_Pres_Proud),
    Election_Close_DV = factor(Election_Close),
    Better_worse_DV = factor(Better_worse),
    contacted_by_party_DV = factor(contacted_by_party),
    Volunteer_work_DV = factor(Volunteer_work),
    Income_DV = factor(Income),
    Party_aff_DV = factor (Party),
    Education_DV = factor(Education),
    Community_work_DV = factor(Community_work),
    Anyone_talk_vote_DV = factor(Anyone_talk_vote),
    Appove_Pres = factor(Approve_President),
    Voted_Y_N_DV = ifelse(Voted_Y_N > 1, 1, 0),
    Country_direction_DV = ifelse(Country_direction > 1, 0, 1)
  )

```  

```{r}
# Import data to merge: State voting access ranking and competativeness of elections

Voter_Access_Comp_Rankings <- read_excel("Voter Access-Comp Rankings.xlsx")
```

```{r}
Data_Final_REG <- left_join(
  Final_DS_DV,
  Voter_Access_Comp_Rankings,
  by = c("YEAR", "State")
)

# Checking that merge occured properly- did not add any new observations 
nrow(Final_DS_DV) == nrow(Data_Final_REG)

# Checking for duplications (VCF0006 is the Study Respondent Number)
janitor::get_dupes(anes_timeseries_cdf_stata13, VCF0004, VCF0006)

get_dupes(Data_Final_REG, YEAR, VCF0006)
```

# Logit Regressions  
```{r}

# Basic Logit Regression 

reg_wsr <- glm(Voted_Y_N_DV ~ Age_Dummy  + Gender_DV + Race_DV + Income_DV+ Education_DV + bw_parties_DV + Party_aff_DV  +  Control_split_DV + Election_Close_DV + Anyone_talk_vote_DV  + Contacted_by_party_DV +  Contacted_Dem_Party_DV + Contacted_Rep_Party_DV + Better_worse_DV + Country_direction_DV    + Dem_Pres_Angry_DV  + Dem_Pres_hopeful_DV + Dem_Pres_Proud_DV + Dem_Pres_Afraid_DV + Rep_Pres_Angry_DV  + Rep_Pres_hopeful_DV  +  Rep_Pres_Proud_DV+ Rep_Pres_Afraid_DV   + Interest_elec_DV  + Volunteer_work_DV +Party_aff_DV + RANKING + PercentDiff, weights= Weights, family= binomial, data=Data_Final_REG)

summary(reg_wsr)

# Used the margin commons to account for that the logit regression gives an output off one baseline, and this helps normalize the logit regression to reflect how the variables can shift and impact one and other

margin_reg <- margins(reg_wsr)

summary (margin_reg)
```

# Linear Regression Model 
```{r}

reg_wsr_LM <- lm(Voted_Y_N_DV ~ Age_Dummy  + Gender_DV + Race_DV + Income_DV+ Education_DV + bw_parties_DV + Party_aff_DV  +  Control_split_DV + Election_Close_DV + Anyone_talk_vote_DV  + Contacted_by_party_DV + Contacted_Dem_Party_DV + Contacted_Rep_Party_DV + Better_worse_DV + Country_direction_DV + Dem_Pres_Angry_DV  + Dem_Pres_hopeful_DV + Dem_Pres_Proud_DV + Dem_Pres_Afraid_DV + Rep_Pres_Angry_DV + Rep_Pres_hopeful_DV  +  Rep_Pres_Proud_DV+ Rep_Pres_Afraid_DV + Interest_elec_DV  + Volunteer_work_DV +Party_aff_DV + RANKING + PercentDiff, weights= Weights, data=Data_Final_REG)

summary(reg_wsr_LM)

# We ran the linear and logit regression models to compare the two. The Logit Regression based on statistical technicalities fits a binary dependent variable better, yet when one uses the margin command to normalize the results of the logit regression, the two produce extremely similar results. 
```

```{r}
# Turn OLS Regression into a DF to calculate the percentage changes from the baseline 
Regression <- tidy(reg_wsr)

OLS_DF <- tidy(reg_wsr_LM)

# Calculate the level of the vairable's impact by summing the coefficient with the OLS intercept
OLS_DF <- mutate(OLS_DF, Level_of_coef=(0.4197571788+estimate))

# Calculate the percent change between the impact of the variable and the baseline

OLS_DF <- mutate(OLS_DF, Percent_Change=((Level_of_coef-0.4197571788)/0.4197571788))

# Adding a Column to denote category so it is easier to filter and create visualizations 

OLS_DF <- OLS_DF  %>% mutate(Variable2 = c("Intercept","Age_Dummy","Age_Dummy","Age_Dummy","Age_Dummy","Age_Dummy","Age_Dummy","Gender_DV","Gender_DV","Race_DV","Race_DV","Race_DV","Income_DV","Income_DV","Income_DV","Income_DV","Income_DV","Education_DV","Education_DV","Education_DV","bw_parties_DV","bw_parties_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Control_split_DV","Control_split_DV","Election_Close_DV","Election_Close_DV","Anyone_talk_vote_DV","Anyone_talk_vote_DV","Contacted_by_party_DV","Contacted_by_party_DV","Contacted_by_party_DV","Contacted_by_party_DV","Contacted_by_party_DV","Better_worse_DV","Better_worse_DV","Country_direction_DV","PRES_FEELING1","PRES_FEELING1","PRES_FEELING2","PRES_FEELING2","PRES_FEELING1","PRES_FEELING1","PRES_FEELING2","PRES_FEELING2","Interest_elec_DV","Interest_elec_DV","Interest_elec_DV","Volunteer_work_DV","Volunteer_work_DV","RANKING","PercentDiff"))

```

# Building visualizations 
# Graphs of percentage changes
```{r}

# Percent Change in Age Graph

Percent_AGE <- OLS_DF %>% filter(Variable2 =="Age_Dummy")
Percent_AGE <- mutate(Percent_AGE, Variable = c("25-34","35-44","45-54","55-64","65-74","75+"))

Age_Per_Plot <- ggplot(Percent_AGE) + 
  aes(x =Variable, y = Percent_Change) + 
  labs(title = "                        As age increaes so does the likelihood of voting",
              caption = "Source: ANES",
              x = "Age", y = "Percent Change compared to 17-24 Year Old Group") +
  geom_col(fill="#FF9999", colour="blue")  + coord_flip()
Age_Per_Plot

```

```{r}
# Percent change in Education - Graph 
Percent_EDU <- OLS_DF %>% filter(Variable2 =="Education_DV")
Percent_EDU <- mutate(Percent_EDU, Variable = c("High School","College Started (Not Finished) ","College Degree"))

EDU_Per_Plot <- ggplot(Percent_EDU) + 
  aes(x =Variable, y = Percent_Change) + 
  labs(title = "As Education increaes so does the likelihood of voting",
              caption = "Source: ANES",
              x = "Education", y = "Percent Change compared to Non High School Graduates") +
  geom_col(fill="#FF9999", colour="blue", order="ascending")  + coord_flip()
EDU_Per_Plot
```

```{r}
# Percent change based on emotional response - Graph 
Percent_FEELING <- OLS_DF %>% filter(Variable2 =="PRES_FEELING2")
Percent_FEELING <- mutate(Percent_FEELING, Variable = c("Dem Evokes Pride", "Dem Evokes Fear","Rep Evokes Pride", "Rep Evokes Fear"))

Percent_FEELING <- mutate(Percent_FEELING, Percent_Change2=(0.4197571788+Percent_Change))
Percent_FEELING <- mutate(Percent_FEELING, Percent_Change3= (0.4197571788-Percent_Change2)/(Percent_Change2))


Feeling_Per_Plot <- ggplot(Percent_FEELING) + 
  aes(x =Variable, y = Percent_Change3) + 
  labs(title = "What Emotions Motivate Potential Voters",
              caption = "Source: ANES",
              x = "Emotions Elicited?", y = "Percent Change") +
  geom_col(fill="#FF9999", colour="blue") + coord_flip()  
Feeling_Per_Plot

```

# Odds Ratio Charts based off the Logit Regressions
```{r}

  
# Tibble method to make ODDS RATIO CHARTS based off the LOGIT Regressions
Reg_OR_Table <-  tbl_regression(
  reg_wsr,
  exponentiate = TRUE)

# DF with Odds Ratios and CI

plot_data_3<- Reg_OR_Table %>%
  as_tibble() %>%
  janitor::clean_names() %>%
  mutate(Variable = c("Age_Dummy","17-24","25-34","35-44","45-54","55-64","65-74","75+","Gender_DVGender_DV","Gender_DV1","Gender_DV2","Gender_DV3","Race_DVRace_DV","Race_DV1","Race_DV2","Race_DV3","Race_DV4","Income_DVIncome_DV","Income_DV1","Income_DV2","Income_DV3","Income_DV4","Income_DV5","Income_DV6","Education_DVEducation_DV","Education_DV1","High School","Some College","College Degree", "bw_parties_DVbw_parties_DV", "bw_parties_DV1","bw_parties_DV2", "bw_parties_DV9", "Party_aff_DVParty_aff_DV", "Party_aff_DV1","Party_aff_DV2", "Party_aff_DV3","Party_aff_DV4", "Party_aff_DV5", "Party_aff_DV6","Party_aff_DV7","Control_split_DVControl_split_DV","Control_split_DV1","Control_split_DV2","Control_split_DV3","Election_Close_DVElection_Close_DV","Election_Close_DV1","The Presidential Election Will Be a Close race","Dont Know", "Anyone_talk_vote_DVAnyone_talk_vote_DV", "Yes-Talked About Election","Anyone_talk_vote_DV3","No- I Did not Talk About the Election With Anyone", "Contacted_by_party_DVContacted_by_party_DV", "Contacted_by_party_DV1", "Contacted_by_party_DV2", "Contacted_by_party_DV3", "Contacted_Dem_Party_DVContacted_Dem_Party_DV", "Contacted_Dem_Party_DV1", "Contacted_Dem_Party_DV2", "Contacted_Dem_Party_DV3", "Contacted_Rep_Party_DVContacted_Rep_Party_DV", "Contacted_Rep_Party_DV1", "Contacted_Rep_Party_DV2", "Contacted_Rep_Party_DV3", "Better_worse_DVBetter_worse_DV","Better Now","Same","The Country is Worse Now", "Country_direction_DVCountry_direction_DV", "Dem_Pres_Angry_DVDem_Pres_Angry_DV", "Dem_Pres_Angry_DV1", "Dem_Pres_Angry_DV2","Dem_Pres_Angry_DVDem_Pres_hopeful_DV","Dem_Pres_hopeful_DV1","Dem_Pres_hopeful_DV2","Dem_Pres_Proud_DVDem_Pres_Proud_DV","Dem_Pres_Proud_DV1","Dem_Pres_Proud_DV2","Dem_Pres_Afraid_DVDem_Pres_Afraid_DV","Dem_Pres_Afraid_DV1","Dem_Pres_Afraid_DV2","Rep_Pres_Angry_DVRep_Pres_Angry_DV","Rep_Pres_Angry_DV1","Rep_Pres_Angry_DV2","Rep_Pres_hopeful_DVRep_Pres_hopeful_DV","Rep_Pres_hopeful_DV1","Rep_Pres_hopeful_DV2","Rep_Pres_Proud_DVRep_Pres_Proud_DV","Rep_Pres_Proud_DV1","Rep_Pres_Proud_DV2","Rep_Pres_Afraid_DVRep_Pres_Afraid_DV","Rep_Pres_Afraid_DV1","Rep_Pres_Afraid_DV2","Interest_elec_DVInterest_elec_DV","Interest_elec_DV1","Interest_elec_DV2","Interest_elec_DV3","Interest_elec_DV9","Volunteer_work_DVVolunteer_work_DV","Volunteer_work_DV1","Volunteer_work_DV2","Volunteer_work_DV3","RANKINGRANKING","PercentDiff"))

# Filtered DF with Odds Ratios and CI 

plot_data_new_cat <- plot_data_3  %>% mutate(Variable2 = c("Age_Dummy",
"Age_Dummy", "Age_Dummy","Age_Dummy","Age_Dummy","Age_Dummy","Age_Dummy","Age_Dummy","Gender_DV","Gender_DV","Gender_DV","Gender_DV","Race_DV","Race_DV","Race_DV","Race_DV","Race_DV","Income_DV","Income_DV","Income_DV","Income_DV","Income_DV","Income_DV","Income_DV","Education_DV","Education_DV","Education_DV","Education_DV","Education_DV","bw_parties_DV","bw_parties_DV","bw_parties_DV","bw_parties_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Party_aff_DV","Control_split_DV","Control_split_DV","Control_split_DV","Control_split_DV","Election_Close_DV","Election_Close_DV","Election_Close_DV","Election_Close_DV","Anyone_talk_vote_DV","Anyone_talk_vote_DV","Anyone_talk_vote_DV","Anyone_talk_vote_DV","Contacted_by_party_DV","Contacted_by_party_DV","Contacted_by_party_DV","Contacted_by_party_DV","Contacted_Dem_Party_DV","Contacted_Dem_Party_DV","Contacted_Dem_Party_DV","Contacted_Dem_Party_DV","Contacted_Rep_Party_DV","Contacted_Rep_Party_DV","Contacted_Rep_Party_DV","Contacted_Rep_Party_DV","Better_worse_DV","Better_worse_DV","Better_worse_DV","Better_worse_DV","Country_direction_DV","Dem_Pres_Angry_DV","Dem_Pres_Angry_DV","Dem_Pres_Angry_DV","Dem_Pres_Angry_DV","Dem_Pres_hopeful_DV","Dem_Pres_hopeful_DV","Dem_Pres_Proud_DV","Dem_Pres_Proud_DV","Dem_Pres_Proud_DV","Dem_Pres_Afraid_DV","Dem_Pres_Afraid_DV","Dem_Pres_Afraid_DV","Rep_Pres_Angry_DV","Rep_Pres_Angry_DV","Rep_Pres_Angry_DV","Rep_Pres_hopeful_DV","Rep_Pres_hopeful_DV","Rep_Pres_hopeful_DV","Rep_Pres_Proud_DV","Rep_Pres_Proud_DV","Rep_Pres_Proud_DV","Rep_Pres_Afraid_DV","Rep_Pres_Afraid_DV","Rep_Pres_Afraid_DV","Interest_elec_DV","Interest_elec_DV","Interest_elec_DV","Interest_elec_DV","Interest_elec_DV","Volunteer_work_DV","Volunteer_work_DV","Volunteer_work_DV","Volunteer_work_DV","RANKING","PercentDiff")) %>%
filter(!is.na(or))

# DF with just Odds Ratios for AGE
  
OR_AGEs <- plot_data_new_cat %>% filter(Variable2 =="Age_Dummy")

# Plot for Age Odds Ratios
OR_Age_Plot <- ggplot(OR_AGEs) + 
  aes(x =Variable, y = or) + 
  labs(title = "Effect of Age on Voting",
              caption = "Source: ANES",
              x = "Age", y = "Odds Ratio") +
  geom_col(fill="#FF9999", colour="blue") + 
  coord_flip()  
OR_Age_Plot

# DF with just Odds Ratios for Education
OR_EDU <- plot_data_new_cat %>% filter(Variable2 =="Education_DV")

# Plot for Education Odds Ratios

OR_Edu_Plot <- ggplot(OR_EDU) + 
  aes(x =Variable, y = or) + 
  labs(title = "Effect of Education on Voting",
              caption = "Source: ANES",
              x = "Education", y = "Odds Ratio") +
  geom_col(fill="#FF9999", colour="blue") + 
  coord_flip()  
OR_Edu_Plot

# DF with just Odds Ratios for several categories 
OR_Mixed <- plot_data_new_cat %>% filter(Variable2 =="Election_Close_DV" & characteristic== "2"  | Variable2=="Anyone_talk_vote_DV" & characteristic== "5" | Variable2=="Better_worse_DV" & characteristic== "3")

# Plot for for several categories

OR_Mixed_Plot <- ggplot(OR_Mixed) + 
  aes(x =Variable, y = or) + 
  labs(caption = "Source: ANES",
              x = "", y = "Odds Ratio") +
  geom_col(fill="#FF9999", colour="blue") + 
  coord_flip()  
OR_Mixed_Plot

``` 

# BARCHARTS!
```{r}

# Barplot- Slide 7- Voting and Difference Between Parties

# Weighting survey Data  
Data_svy <- as_survey_design(Data_Final_REG, weights = Weights)
augment(reg_wsr, data = Data_Final_REG) %>% 
  select(Contacted_Dem_Party_DV, Rep_Pres_Proud_DV)


Plot_Diffbw_Party<- Data_svy %>%
  group_by(Bw_parties) %>%
  summarise(new_col = survey_mean(Voted_Y_N_DV, vartype="ci", na.rm = TRUE)) %>%
  filter(Bw_parties=="2" |Bw_parties=="1") %>%
  mutate(Variable2 = c("No Difference", "Yes, there is a difference"))
  
Plot_Diffbw_Party

Diff_Parties <- ggplot(Plot_Diffbw_Party) +
  aes(x =Variable2, y = new_col, ymin = new_col_low, ymax = new_col_upp) +
   geom_col(position="dodge", fill="#FF9999", colour="blue", Width=.1, stat='identity') +  labs(caption = "Source: ANES", x = "Is there a difference between parties", y = "Percent that voted", size =12) + 
  geom_errorbar(ymin=0,ymax=0)

Diff_Parties

Plot_DiffELECCLO <- Data_svy %>%
  group_by(Election_Close) %>%
  summarise(new_col = survey_mean(Voted_Y_N_DV, vartype="ci", na.rm = TRUE)) %>%
  filter(Election_Close=="1" |Election_Close=="2") %>%
  mutate(Variable2 = c("Will win by quite a bit", "Close Race"))

Plot_DiffELECCLO

Elections_Close_GRAPH <- ggplot(Plot_DiffELECCLO) +
  aes(x =Variable2, y = new_col, ymin = new_col_low, ymax = new_col_upp) +
   geom_col(position="dodge", fill="#FF9999", colour="blue", Width=.1, stat='identity') +  labs(caption = "Source: ANES", x = "Will the Presidential Election Be Close", y = "Percent that voted", size =12) + 
  geom_errorbar(ymin=0,ymax=0)

Elections_Close_GRAPH

```


