---
title: "MZ Review"
output:
  github_document: default
  word_document: default
---

```r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Would not knit with this code- need to fix
```

#Install packages if first time
```{r eval=FALSE}
install.packages('dplyr')
install.packages('readr')
install.packages('tidyr')
install.packages('stringr')
install.packages('forcats')
install.packages('purr')
install.packages("ggpubr")
install.packages('car')
install.packages('gdata')
install.packages("skimr")
```

```r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Read in Packages needed
```{r message=FALSE}
library(dplyr) # manipulate dataframes
library(readr) # read/write dataframes
library(tidyr) # reshaping dataframes
library(stringr) # string manipulation
library(forcats) # factor manipulation
library(purrr) # iteration (instead of loops)
library(ggpubr) # for Correlation
library('ggplot2') # for Plots
library ('car')
library ('gdata')
library('skimr') 
```

# Does not read this- need to fix data import for reproducibilty

# Import the data- ANES Survey Timeseries
# Unzip the ANES data if needed
```{r}
source("unzip-anes-data.r")
```

```{r}
library(haven)
anes_timeseries_cdf_stata13 <- read_dta("data-raw/anes_timeseries_cdf_stata13.dta")
```
# Filtering for the right years 
```{r}
June_DS <-anes_timeseries_cdf_stata13[!(anes_timeseries_cdf_stata13$VCF0004<"2004"),]
```

```{r}
# Removing Labels

June_DS %>% 
  zap_labels() %>% 
  select(
    VCF0102,
    VCF0104, 
    VCF0880, 
    VCF0606, 
    VCF0501,
    VCF9030a,
    VCF9206, 
    VCF0105b, 
    VCF0450, 
    VCF0301,  
    VCF9206, 
    VCF9202,
    VCF0358, 
    VCF0360, 
    VCF0370, 
    VCF0372, 
    VCF9253, 
    VCF0714, 
    VCF9256, 
    VCF0900b, 
    VCF0114, 
    VCF9021,  
    VCF9030b,
    VCF9030c,	  
    VCF9222, 
    VCF0901a,
    VCF0009z,
    VCF0310,
    VCF0358,
    VCF0360,
    VCF0370,
    VCF0372,
    VCF0702,
  ) %>% 
  skim()

```

# Filtering the Dataset for the right variables
```{r}

July_DS_1 = subset(June_DS, select = c(VCF0102,
    VCF0104,
    VCF0004,
    VCF0702,
    VCF0880, 
    VCF0606, 
    VCF0501,
    VCF9030a,
    VCF9206, 
    VCF0105b, 
    VCF0450, 
    VCF0301,  
    VCF9202,
    VCF0358, 
    VCF0360, 
    VCF0370,
    VCF0310,
    VCF0372, 
    VCF0714, 
    VCF9256, 
    VCF0900b, 
    VCF0114, 
    VCF9030b,
    VCF9030c,	  
    VCF9222,
    VCF9021,
    VCF9201,
    VCF0901a,
    VCF0009z))
```

# Dealing w/ missings # For many of the categories I added a "Dummy" category to signal the question was unanswered. If the regression shows these dummies are not significant, can assume that these missings were not strongly biased in a direction. 
```{r}

July_DS_1 <- July_DS_1 %>%
   mutate(
   VCF0501 = replace_na(VCF0501, 9),
    VCF9256 = replace_na(VCF9256, 3),
    VCF9030b =  replace_na(VCF9030b, 3),
    VCF9030c =  replace_na(VCF9030c, 3),
    VCF0114 = replace_na(VCF0114, 6),
    VCF0310 = replace_na(VCF0310, 9),
    VCF9021 =  replace_na(VCF9021, 3))
        

```
  
summary("Gender")

```{r}
 
July_DS_1 <- July_DS_1 %>% 
    rename(
    control_split = VCF9206,
    Voted_Y_N = VCF0702,
    Race = VCF0105b,
    Interest_Elec = VCF0310,
    Weights = VCF0009z,
    Dem_Pres_Angry = VCF0358,
    Dem_Pres_hopeful= VCF0360,
    Rep_Pres_Angry = VCF0370,
    Rep_Pres_hopeful = VCF0372,
    Election_Close = VCF0714,
    Age = VCF0102,
    Gender = VCF0104,
    Better_worse = VCF0880,
    FED_Tax = VCF0606,
    Bw_parties = VCF0501,
    contacted_by_party = VCF9030a,
    Volunteer_work = VCF9256,
    State_CD = VCF0900b,
    Income = VCF0114,
    Contacted_Dem_Party = VCF9030b,
    Contacted_Rep_Party =VCF9030c,	 	 	 		
		Country_direction = VCF9222,
    State = VCF0901a,
		Approve_President = VCF0450, 
    Party = VCF0301,
		Anyone_talk_vote = VCF9021,
		Like_dislike_Rep_party = VCF9202,
		YEAR = VCF0004, 
		Like_dislike_Dem_party = VCF9201
)

```


# Creating Dummy Variables
```{r}
   
    Final_DS_DV <- July_DS_1 %>% 
    mutate(
    Age_Dummy = factor(Age),
    Interest_elec_DV = factor(Interest_Elec),
    Gender_DV = factor(Gender),
    bw_parties_DV = factor(Bw_parties),
    Contacted_by_party_DV = factor(contacted_by_party),
    Contacted_Dem_Party_DV = factor(Contacted_Dem_Party),
    Contacted_Rep_Party_DV= factor(Contacted_Rep_Party),
    Control_split_DV = factor(control_split),
    Race_DV = factor(Race),
    Dem_Pres_Angry_DV = factor(Dem_Pres_Angry),
    Dem_Pres_hopeful_DV =factor(Dem_Pres_hopeful),
    Rep_Pres_Angry_DV = factor(Rep_Pres_Angry),
    Rep_Pres_hopeful_DV = factor(Rep_Pres_hopeful),
    Election_Close_DV = factor(Election_Close),
    Better_worse_DV = factor(Better_worse),
    contacted_by_party_DV = factor(contacted_by_party),
    Volunteer_work_DV = factor(Volunteer_work),
    Income_DV = factor(Income),
    Anyone_talk_vote_DV =factor(Anyone_talk_vote),
    Appove_Pres = factor(Approve_President),
    Voted_Y_N_DV = ifelse (Voted_Y_N > 1, 1, 0),
    Country_direction_DV = ifelse (Country_direction > 1, 0, 1)
  )
```  

```{r}
Data_State_rank <- left_join(
  Final_DS_DV, 
  Voter_Access_Comp_Rankings, 
  by = c("YEAR", "State")
)

names(Data_State_rank)

```

# Regression 
```{r}
reg_DV <- lm(Voted_Y_N_DV ~ Age_Dummy + Gender_DV + Race_DV + bw_parties_DV + Contacted_by_party_DV + Control_split_DV + Election_Close_DV + Anyone_talk_vote_DV +Contacted_Dem_Party_DV+ Contacted_Rep_Party_DV+ Better_worse_DV + bw_parties_DV + Volunteer_work_DV  + Income_DV + Dem_Pres_Angry_DV + Dem_Pres_hopeful_DV + Rep_Pres_Angry_DV + Rep_Pres_hopeful_DV + Interest_elec_DV + Country_direction_DV, weights= Weights, data=Final_DS_DV)

reg_wsr <- lm(Voted_Y_N_DV ~ Age_Dummy + Gender_DV + Race_DV + bw_parties_DV + Contacted_by_party_DV + Control_split_DV + Election_Close_DV + Anyone_talk_vote_DV +Contacted_Dem_Party_DV+ Contacted_Rep_Party_DV+ Better_worse_DV + bw_parties_DV + Volunteer_work_DV  + Income_DV + Dem_Pres_Angry_DV + PercentDiff + Dem_Pres_hopeful_DV + Rep_Pres_Angry_DV + Rep_Pres_hopeful_DV + Interest_elec_DV + RANKING +  Country_direction_DV, weights= Weights,data=Data_State_rank)

summary(reg_wsr)

summary(reg_DV)

``` 

```{r
# Not working with knit- (seemed to work otherwise)
Table1 <- table(Voted_Y_N, Race) 

table(VCF0501)

table(VCF0702, Bw_parties)

Dem_Voters <- table(VCF0702, VCF0314)
round(prop.table(Dem_Voters,1),2)

Diff_parties <- table(VCF0702, VCF0501)
Diff_parties
round(prop.table(Diff_parties,1),2)

Dislike_DEM <- table(VCF0702, VCF9201)
Dislike_DEM

Dislike_REP <- table(VCF0702, VCF9202)

Rep_views <- table(VCF0702, VCF9203)
round(prop.table(Rep_views,1),2)

which_party <- table(VCF0702, VCF9204)
round(prop.table(which_party,1),2)

Party_pref <- table(VCF0702, VCF9206)
round(prop.table(Party_pref,1),2)

Dem_Smart <- table(VCF0702, VCF0350)
round(prop.table(Dem_Smart,1),2)

Dem_Angry <- table(VCF0702, VCF0358)
round(prop.table(Dem_Angry,1),2)

REP_Angry <- table(VCF0702, VCF0370)
round(prop.table(REP_Angry,1),2)

Approve_Pres <- table(VCF0702, VCF0450)
round(prop.table(Approve_Pres,1),2)

Approve_Pres_rating <- table(VCF0702, VCF0451)
round(prop.table(Approve_Pres_rating,1),2)

Pres_Econ <- table(VCF0702, VCF9220)
round(prop.table(Pres_Econ,1),2)

Right_Track <- table(VCF0702, Country_direction)
round(prop.table(Right_Track,1),2)

LIB_CON <- table(VCF0702, VCF0803)
round(prop.table(LIB_CON,1),2)

Trust_Fed_Gov <- table(VCF0702, VCF0604)
round(prop.table(Trust_Fed_Gov,1),2)

Crooked_FED <- table(VCF0702, VCF0608)
round(prop.table(Crooked_FED,1),2)

TRUST_GOV_GEN <- table(VCF0702, VCF0656)
round(prop.table(TRUST_GOV_GEN,1),2)

Volunteer <- table(VCF0702, VCF9256)
round(prop.table(Volunteer,1),2)

Interst_Elec <- table(VCF0702, VCF0310)
round(prop.table(Interst_Elec,1),2)

Care_win <- table(VCF0702, VCF0311)
round(prop.table(Care_win,1),2)

Care_win_CONG <- table(VCF0702, VCF0312)
round(prop.table(Care_win_CONG,1),2)

Your_econ <- table(VCF0702, Better_worse)
round(prop.table(Your_econ,1),2)

Pred_Close <- table(VCF0702, VCF0714)
round(prop.table(Pred_Close,1),2)

barplot(Care_win, col=c("Purple","blue"),
       beside=T,
       main="What motivates voters?",
    legend= c("No Difference", "Difference"),  
       ylab= "Voted?",
       xlab= "Is there a difference between the two major parties", 
    las=1)
```

```{r}

